\dppTitle

### 2014-06-02 manuscripts/dpp-msbayes/reviews/response.tex

% \makeatletter
% \renewcommand{\section}{\@startsection{section}{1}{0mm}%
%     {-8pt}%
%     {4pt}%
% {\sffamily\large\itshape}}
% \makeatother

\begin{document}
% \raggedright
\setlength{\parindent}{0in}

I greatly appreciate the helpful comments of the editor and reviewers. In this
document, I provide responses to these comments, including descriptions of the
changes I have made.

\section{Editor's Comments}\label{ed}
\setcounter{commentCounter}{0}
\revcomment{
    Looking at Reviewer 2's list of issues, they appear to relate only to the
    presentation, and Reviewer 2 is not asking for more analysis.  These
    requests for revision are requests for comments, clarifications, and
    statements of caveats to be made by the author.  I think that if these
    requests are attended to then the ms will be improved.
}
\response{
    Reviewer 2's comments were very helpful, and have improved the clarity of
    the manuscript. Below, in Section \ref{rev2}, I address each of Reviewer
    2's concerns along with the corresponding changes I have made in light of
    the comments.
}

\revcomment{
    (Concerning Reviewer 2's comment 1.  I did not get the impression that the
    author was criticizing Bayesian foundations, but this Reviewer did, and
    that in itself shows that there is room for misunderstanding.  I suspect
    that the author may feel that the intention of the paragraph is clear
    enough, but perhaps the wording here can be adjusted in the light of this
    reviewer's comment to more clearly say that you are talking about options
    for prior choice, that msBayes has opted for uniform priors, and your
    comments on that.)
}
\response{
    I agree that there was room for misunderstanding given that the context of
    the statements were not made clear. Please see Section \ref{rev2} below for
    the specific edits I have made in response to this helpful comment.
}

### 2014-06-02 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Another tweak to the dpp ms results section.
*Now*, it should be ready for re-submission.

Figure \ref{figNegrosPanay} shows the estimated posterior probability
distribution over the number of divergence events when the data from the
nine-taxon pairs from the Islands of Negros and Panay are analyzed under DPP
models that sample over unordered (\npModelDPP) and ordered
(\npModelDPPOrdered) models of divergence.
The results are similar under both models and, again, yield a large amount of
uncertainty about the number of divergence events that is similar to the prior
uncertainty.
Both models estimate a similar set of 10 unordered divergence models with the
highest posterior probability
(Figures~S\labelcref{figDivModelsNP,figDivModelsNPOrdered}).

The main advantage of the \npModelDPPOrdered over the \npModelDPP is that the
identity of the taxa is maintained, and thus a fully marginalized estimate of
divergence times across the taxa can be obtained
(Figure~S\ref{figMarginalTimes}).
Furthermore, the probability of co-divergence among any set of taxa can be
estimated from the posterior sample.

>>>>

Figure \ref{figNegrosPanay} shows the estimated posterior probability
distribution over the number of divergence events when the data from the
nine-taxon pairs from the Islands of Negros and Panay are analyzed under DPP
models that sample over unordered (\npModelDPP) and ordered
(\npModelDPPOrdered) models of divergence.
The results are similar under both models and, again, yield a large amount of
uncertainty about the number of divergence events that is similar to the prior
uncertainty.
\change{
The small difference between the results of the \npModelDPP and
\npModelDPPOrdered models is consistent across multiple analyses, and thus
could be due to error introduced to the \npModelDPP model by the invalid
shuffling of the summary statitic vectors.
}
Both models estimate a similar set of 10 unordered divergence models with the
highest posterior probability
(Figures~S\labelcref{figDivModelsNP,figDivModelsNPOrdered}).

\change{
The main advantages of the \npModelDPPOrdered model over the \npModelDPP are
that
(1) the incorrect shuffling of the summary statistic vectors is avoided,
(2) the identity of the taxa is maintained, and thus a fully marginalized
estimate of divergence times across the taxa can be obtained
(Figure~S\ref{figMarginalTimes}), and
(3) the probability of co-divergence among any set of taxa can be
estimated from the posterior sample.
}
